---
title: "Wealth and Health"
author: "Christian Coffman"
date: "10/1/2020"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(ggplot2)
library(tidyr)

mydata <- read.csv2('/home/christian/Downloads/dfa-networth-levels.csv', header = TRUE, sep = ",") %>%
  select(Date, Net.worth, Category)

```

```{r}
ggplot(mydata, aes(x=Date, y = Net.worth, col = Category)) +
  geom_point()
```


Transform back to the average wealth per person in each category. (Actually it's normalzied per percent popoulation, but it's same thing different scale)
```{r}
wid <- mydata %>% 
  spread(Category, Net.worth)

wid <- wid %>%
  mutate(Ave_bot50 = Bottom50 / 50, Ave_Next40 = Next40/40, Ave_Next9 = Next9/9, Ave_top1 = Top1) %>%
  mutate(b50p = Ave_bot50/Ave_top1, n40p= Ave_Next40/Ave_top1, n9r= Ave_Next9/Ave_top1) %>%
  mutate(rate50 = 1/(1 + exp(-b50p))  , rate40= 1/(1 + exp(-n40p)), rate9= n9r)

  
  
wid %>% 
  gather(Category, Ave_worth, Ave_bot50:Ave_top1) %>%
  ggplot(aes(x=Date, y=Ave_worth, col = Category)) +
  geom_point() # + scale_y_log10()
  
wid %>% 
  gather(Category, Rates, rate50:rate9) %>%
  ggplot(aes(x=Date, y=Rates, col = Category)) +
  geom_point() +
  ggtitle("Rate of having difficulties with medical bills")
```

Assume Proportion of visits scales with $$ P=1-\frac{1}{1+e^{-(a+bx)}}) $$ where P is the proportion, a is some constant lets say 0 for now, and b is some constant proportion, so lets say 0.5... Let's see what happens to the transformed data. Let x represent the percentile in social system.
```{r} 
wid %>%
  gather(Category, Propor, b50p:n9r) %>%
  ggplot(aes(x=Date, y=Propor, col = Category)) +
  geom_point()
p <- 1/(1 + exp(-x))
plot(x, p)
```